---
title: "Untitled"
output: html_document
---

```{r bio239 line 6, include = FALSE, echo = FALSE}
require(tidyverse)
require(knitr)
```

<div style = "margin-bottom:50px;">

Download the package `tidyverse`

</div>

<div style = "margin-bottom:50px;">
```{r bio239 line 12, echo = FALSE}
data <- read.csv("bio239_spring2022.csv")
knitr::kable(head(data[, 1:5]), "pipe")
```
</div>

<div style = "margin-bottom:50px;">
```{r bio239 line 20, include = FALSE, echo = FALSE}
data3 <- read.csv("bio239_spring2022b.csv")
data3
```
</div>

<div style = "margin-bottom:50px;">
```{r bio239 line 27, include = TRUE, echo = FALSE}
data3 <- as_tibble(data3)
data3
```
</div>

<div style = "margin-bottom:50px;">

The starting model contains, as its predictors, the main effect of the response
factor (in our study, the species of insect at a site, or mound) and the main effects
and and mutual interactions of th explanatory factors. The response variable in this model
is the counts. We set up the null model (with a Poisson distribution and an implicit log 
link function) as follows:

</div>

<div style = "margin-bottom:50px;">
```{r bio239 line 34, include = TRUE, echo = FALSE}
glm.x0 <- glm( count ~ species + season * mound, data = data3, family = poisson)
```
</div>
















